---
docname: Curriculum Vitae
name: |
  | \huge\textbf{Gera Flores Sempertegui}
#profilepic:
position: |
  | \scriptsize INDUSTRIAL ENGINEER MBA · SENIOR DATA & AI EXECUTIVE · ANALYTICS LEADER · DIGITAL STRATEGY 
#address:
phone: (+51) 948425000
email: "gflores1092@gmail.com"
linkedin: gflores1092
#github: gflores1092
#www: https://linktr.ee/yeraflores
headcolor: 414141
output: 
  vitae::awesomecv:
    keep_tex: true
always_allow_html: yes
header-includes:
  - \usepackage{parskip}
  - \usepackage{ragged2e}
  - \usepackage{changepage}
  - \usepackage{setspace}
  - \definecolor{awesome}{HTML}{0066CC}
  - \definecolor{text}{HTML}{0066CC}
  - \usepackage{graphicx}
  - \usepackage{geometry}
  - \geometry{left=1.5cm, right=1.5cm, top=1cm, bottom=1cm}

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
library(vitae)
library(xtable)
library(tidyverse)
```

```{r}
# Select the language (English or Spanish)
lang <- "English"  # Change to "Spanish" for the Spanish version
```

```{r}

# Functions

#tabular function
tabular <- function(tbl,
                    digits = 0,
                    include.colnames = FALSE,
                    include.rownames = FALSE,
                    hline.after = NULL,
                    size = getOption("xtable.size", NULL),
                    add.to.row = getOption("xtable.add.to.row", NULL),
                    ...)
                    {
                      tbl <- tbl %>%
                             mutate_all(
                               ~ if_else(
                                    . == "\\tiny", 
                                    "\\vspace{-0.20cm}", 
                                   paste("\\vspace{0.025cm}\\parbox{18cm}{", ., "}")
                                        )
                                   )
                    
                      tbl %>%
                        xtable(digits = digits, ...) %>%
                        print(include.colnames = include.colnames,
                              include.rownames = FALSE,
                              hline.after = hline.after,
                              comment = FALSE,
                              latex.environments = NULL,
                              floating = FALSE,
                              size = size,
                              add.to.row = add.to.row,
                              sanitize.text.function = function(x) {x}
                        )
                    }

# section function
section_title <- "\\hspace{0.25cm}\\color{black}{\\Large\\faInfoCircle}\\hspace{0.25cm}\\section{" 

# title function
title <- function(text, link = "") {
  if (link != "") {
    return(paste0("\\href{", link, "}{\\normalsize\\textbf{", text, "}}\\hfill"))
  } else {
    return(paste0("\\normalsize\\textbf{", text, "}\\hfill"))
  }
}

# company function
company <- function(text) {
  paste0("\\footnotesize{", text, "}\\hfill")
}

# bullet function
bullet <- function(text) {
  paste0("\\raisebox{+0.2\\height}{\\tiny\\faCircle}\\hspace{0.15cm}\\small{", text, "}\\hfill")
}

# location function
location <- function(text) {
  paste0("\\hfill\\scriptsize\\faMapMarker\\hspace{0.10cm}\\emph{", text, "}\\hfill")
}

# calendar function
calendar <- function(text) {
  paste0("\\hfill\\scriptsize\\faCalendarCheckO\\hspace{0.05cm}", text, sep="")
}

# word function
word <- function(text) {
  paste0("\\hfill\\small{", text, "}")
}

# paragraph function
paragraph <- function(text) {
  paste0("\\small{", text, "}\\hfill")
}

```

```{r}

# Spanish

spanish_sections <- c(
                    "Resumen", 
                    "Experiencia", 
                    "Educación",
                    "Certificados",
                    "Proyectos destacados",
                    "Habilidades técnicas",
                    "Habilidades blandas",
                    "Información adicional"
                    )

# English

english_sections <- c(
                    "Summary", 
                    "Experience", 
                    "Education",
                    "Certifications",
                    "Featured projects",
                    "Hard skills",
                    "Soft skills",
                    "Interests"
                    )
# Remote

remote_sections <- c(
                    "Summary", 
                    "Experience", 
                    "Education",
                    "Certifications",
                    "Featured projects",
                    "Hard skills",
                    "Soft skills",
                    "Interests"
                    )

```

```{r}

# Spanish

spanish_summary <- c(
  "Ejecutiva senior con más de 12 años de experiencia liderando áreas de analítica avanzada, inteligencia artificial y estrategia comercial en empresas multinacionales. Ingeniera industrial con MBA especializada en el desarrollo de soluciones basadas en datos de alto impacto en ingresos, eficiencia y transformación digital. He liderado equipos a nivel LATAM, impulsando una cultura data driven con visión estratégica. Reconocida por su pensamiento analítico y capacidad para escalar operaciones."
)

# English

english_summary <- c(
  "Senior executive with over 12 years of experience leading advanced analytics, artificial intelligence, and commercial strategy areas in multinational companies. Industrial engineer with an MBA specialized in developing data-driven solutions with high impact on revenue, efficiency, and digital transformation. I have led LATAM level teams, driving a data-driven culture with strategic vision. Recognized for analytical thinking and ability to scale operations."
)

# Remote

remote_summary <- c(
  ""
)

```

```{r}

spanish_titles <- c(
                    "Data \\& Analytics Manager", 
                    "Head of Operations", 
                    "Logistics Performance Manager", 
                    "Growth Marketing Lead", 
                    "Analytics Lead",
                    "Experiencia adicional"
                    )

spanish_companies <- c(
                      "MEDIALABTECH",
                      "FALABELLA", 
                      "PEDIDOSYA", 
                      "GLOVO", 
                      "GLOVO",
                      "DIVERSAS EMPRESAS"
                      )

english_titles <- spanish_titles

english_companies <- spanish_companies

remote_titles <- spanish_titles

remote_companies <- spanish_companies

```

```{r}

# Spanish

spanish_bullets <- c(

  #[1]
  "Lideré proyectos estratégicos de analítica avanzada y machine learning a nivel LATAM en Mondelez International.",
  "Implementé modelos predictivos en Google Cloud, mejorando la toma de decisiones comerciales y segmentación regional.",
  "Gestioné la integración y armonización de fuentes comerciales y de marketing en dashboards estratégicos a nivel LATAM.",
  "Fomenté la adopción de prácticas data driven, promoviendo la madurez analítica y estructura de gobernanza regional.",
  
  #[2]
  "Lideré un equipo de 30 personas responsable de la logística, analítica, finanzas y soporte comercial a clientes y vendedores.",
  "Estandaricé y optimicé procesos operativos en Falabella, Tottus, Sodimac y Linio, mejorando la eficiencia hasta en 30\\%.",
  "Desarrollé iniciativas de customer experience, aumentando el CSAT en 15\\% y NPS en 20\\% con estrategias basadas en datos.",
  "Diseñé, ejecuté y gestioné la recuperación de cuentas por cobrar S/. 8 millones con soluciones y desarrollos data driven.",
  "Gestioné presupuestos, control de gastos, transacciones contables y el P\\&L, asegurando el crecimiento y rentabilidad.",
  
  #[3]
  "Lideré un equipo de 5 personas a cargo de la excelencia operativa y el soporte al cliente, socios y repartidores.",
  "Desarrollé modelos que permitieron reducir los tiempos de entrega hasta en 30\\% y optimizar el uso de recursos en 20\\%.",
  "Implementé estrategias data driven para la expansión de operaciones logísticas, aumentando la cobertura en 25\\%.",
  "Incrementé las entregas on-time en 30\\% mediante la optimización de predicción de la demanda, zonas de servicio y rutas.",
  
  #[4]
  "Lideré un equipo multifuncional a cargo de alianzas comerciales, adquisición y retención de clientes y análisis de churn.",
  "Gestioné alianzas estratégicas para mejorar la visibilidad y alcance en el mercado, impulsando su expansión en 30\\%.",
  "Mejoré la UX mediante la optimización del customer journey, aumentando user engagement en 25\\% y conversión en 15\\%.",
  
  #[5]
  "Lideré un equipo data driven para proponer proyectos, estandarizar procesos y generar desarrollos en toda la compañía.",
  "Lideré proyectos de detección de fraudes, monetización de datos y desarrollo de socios, aumentando los ingresos en 20\\%.",
  
  #[6]
  "Consultora de negocios en pequeñas y medianas empresas (pymes) y docente de alumnos de pregrado y postgrado.",
  "En áreas de experiencia del cliente, finanzas y logística en empresas como ENTEL, GOODYEAR, FLSMIDTH y METSO."

)

# English

english_bullets <- c(

  #[1]
  "Led advanced analytics and machine learning strategic projects across LATAM for Mondelez International.",
  "Implemented predictive models in Google Cloud, improving commercial decision-making and regional segmentation.",
  "Managed integration and harmonization of commercial and marketing sources in strategic dashboards across LATAM.",
  "Promoted data driven practices, enhancing analytical maturity and regional governance structure.",
  
  #[2]
  "Led a team of 30 people responsible for logistics, analytics, finance, and commercial support for clients and sellers.",
  "Standardized and optimized operational processes across Falabella, Tottus, Sodimac, and Linio, improving efficiency by up to 30\\%.",
  "Developed customer experience initiatives, increasing CSAT by 15\\% and NPS by 20\\% with data-based strategies.",
  "Designed, executed, and managed the recovery of S/. 8 million in receivables using data-driven solutions.",
  "Managed budgets, expense control, accounting transactions, and the P&L, ensuring growth and profitability.",
  
  #[3]
  "Led a team of 5 people in charge of operational excellence and support to clients, partners, and couriers.",
  "Developed models that reduced delivery times by up to 30\\% and optimized resource use by 20\\%.",
  "Implemented data-driven strategies for logistics expansion, increasing coverage by 25\\%.",
  "Increased on-time deliveries by 30\\% through demand prediction, service zone, and route optimization.",
  
  #[4]
  "Led a cross-functional team in charge of commercial partnerships, customer acquisition and retention, and churn analysis.",
  "Managed strategic partnerships to boost market visibility and reach, driving 30\\% expansion.",
  "Improved UX by optimizing the customer journey, increasing user engagement by 25\\% and conversion by 15\\%.",
  
  #[5]
  "Led a data driven team to propose projects, standardize processes, and develop tools across the company.",
  "Led projects on fraud detection, data monetization, and partner development, increasing revenue by 20\\%.",
  
  #[6]
  "Business consultant for small and medium enterprises (SMEs) and professor for undergraduate and graduate students.",
  "In customer experience, finance, and logistics areas at companies like ENTEL, GOODYEAR, FLSMIDTH, and METSO."
  
)

# Remote

remote_bullets <- c(
  
  #[1]
  "Led a team of 30 people responsible for logistics, analytics, finance, and commercial support to clients and sellers.",
  "Standardized and optimized operational processes at Falabella, Tottus, Sodimac, and Linio, improving efficiency by 20\\%.",
  "Enhanced customer and seller experience, increasing CSAT by 15\\% and NPS by 20\\% with customer-centric strategies.",
  "Led commercial initiatives and training for events like Cyber Days, achieving sales impacts of up to 15\\%.",
  "Designed, executed, and automated the accounts receivable recovery strategy, recovering up to S/. 8 million.",
  "Developed analytical solutions using SQL, R, Python and Google Cloud, reducing operational times and errors up to 50\\%.",
  "Created a data-centric culture, increasing productivity by 60\\% and decision-making accuracy by 30\\%.",
  
  #[2]
  "Led a team of 5 people responsible for operational excellence and support to customers, partners, and couriers.",
  "Developed operational strategies, reducing delivery times by up to 30\\% and optimizing resources by 20\\%.",
  "Designed solutions, predictive models, and automations using SQL, R, and Python, increasing efficiency by 40\\%.",
  "Implemented Machine Learning models to manage fleet availability, increasing revenue by 15\\%.",
  "Increased on-time deliveries by 30\\% through demand prediction, service area, and route optimization.",
  
  #[3]
  "Led a cross-functional team in charge of commercial partnerships, customer acquisition and retention, and churn analysis.",
  "Executed data-driven promotions and recommendations, reducing churn by 20\\% and increasing acquisition by 25\\%.",
  "Managed strategic partnerships to improve market visibility and reach, driving a 30\\% expansion.",
  "Designed and executed specific campaigns that boosted revenue by 20\\% and average ticket size by 10\\%.",
  "Improved UX by optimizing the customer journey, increasing user engagement by 25\\% and conversion by 15\\%.",
  
  #[4]
  "Led a team of Data Analysts and Business Intelligence specialists to propose and develop analytical initiatives.",
  "Directed various data science projects, providing actionable data and increasing operational efficiency by 25\\%.",
  "Led projects for fraud detection, data monetization, and partner development, increasing revenue by 20\\%.",
  "Designed and executed dynamic pricing strategies based on demand and distances, optimizing profitability by 20\\%."
      
)
```

```{r}

# Spanish

spanish_project_titles <- c(
  "Mejora en la gestión de cierres contables y recuperación de cuentas por cobrar y pagar",
  "Control eficiente de gastos e impacto en los resultados del P\\&L",
  "Optimización de la planificación y transporte en la cadena de suministro",
  "Migración de Linio y Falabella Marketplace a Falabella.com",
  "Introducción de nuevos productos en base a comportamiento de clientes"
)

spanish_project_bullets <- c(

  #[1]
  "Lideré, gestioné y mejoré la visibilidad de las Cuentas por Cobrar y Pagar mediante el uso de herramientas analíticas.",
  "Se redujeron los incobrables en 90\\%, se recuperaron S/. 8 millones y se mejoró la gestión contable de los vendedores.",

  #[5] 
  "Desarrollé herramientas y proyecciones y lideré proyectos de mejora de procesos para el control de gastos por conceptos operativos.",
  "Se redujeron los gastos por conceptos operativos hasta en 60\\% y se generaron puntos de control en procesos relacionados.",
  
  #[3]
  "Desarrollé mejoras en la gestión logística mediante el estudio y optimización de variables logísticas.",
  "Se disminuyeron los errores logísticos en 30\\% y mejoraron los resultados en 20\\% al mejorar el cubicaje del transporte.",
  
  #[2]
  "Gestioné y apoyé en la migración de sellers e información en el proyecto de transformación digital a Falabella.com.",
  "Se optimizaron tiempos operativos hasta 90\\% y se recuperaron y activaron cuentas comerciales importantes.",
  
  #[4]
  "Realicé un estudio de comportamiento de clientes basado en compras previas y preferencias como foco de crecimiento.",
  "Se aumentaron los pedidos por cliente en 30\\%, el ticket promedio en 15\\% y se facilitó la introducción de nuevas marcas."
  
)

# English

english_project_titles <- c(
  "Improved management of accounting closures and accounts receivable/payable",
  "Efficient expense control and impact on P\\&L results",
  "Supply chain planning and transport optimization",
  "Migration of Linio and Falabella Marketplace to Falabella.com",
  "New product introductions based on customer behavior"
)

english_project_bullets <- c(
  
  #[1]
  "Led, managed, and improved visibility of Accounts Receivable and Payable using analytical tools.",
  "Uncollectibles reduced by 90\\%, S/. 8 million recovered, and vendor accounting management improved.",

  #[2]
  "Developed tools and forecasts and led process improvement projects for operational expense control.",
  "Reduced operational expenses by up to 60\\% and created control points in related processes.",

  #[3]
  "Developed logistics management improvements through analysis and optimization of logistics variables.",
  "Reduced logistics errors by 30\\% and improved outcomes by 20\\% through better transport cube utilization.",
  
  #[4]
  "Managed and supported the migration of sellers and information during the digital transformation to Falabella.com.",
  "Reduced operational times by up to 90\\% and recovered and reactivated key commercial accounts.",

  #[5] 
  "Conducted customer behavior study based on past purchases and preferences as a growth driver.",
  "Increased orders per customer by 30\\%, average ticket by 15\\%, and facilitated the launch of new brands."
  
)

# Remote

remote_project_titles <- c(
  "Product size classification model",
  "Automation of accounting closing process and recovery of accounts receivable and payable",
  "Predictive model for orders demand",
  "Product recommendation systems for customers",
  "Market basket analysis Machine Learning model"
)

remote_project_bullets <- c(
  
  #[1]
  "Developed a Machine Learning model using Python (TensorFlow) to classify product sizes.",
  "Reduced logistical errors by 30\\% and improved results by 20\\% by enhancing transport cubic capacity.",

  #[2]
  "Implemented the automation of Accounts Receivable and Payable using Google Cloud, SQL, and Python.",
  "Reduced uncollectibles by 90\\%, recovered S/. 8 million, and automated the accounting management for vendors.",

  #[3]
  "Designed a Machine Learning model using Python (TensorFlow) to forecast order demand.",
  "Optimized accuracy up to 95\\% and increased staff earnings by up to 20\\% due to improved efficiency.",
  
  #[4]
  "Developed customer recommendation systems based on previous purchases and preferences using Python (TensorFlow).",
  "Increased orders per customer by 30\\%, average ticket size by 15\\%, and facilitated the introduction of new brands.",

  #[5] 
  "Created a market basket analysis model using Python to generate promotions in the supermarket vertical (mass consumption).",
  "Increased purchase frequency by 20\\%, ticket size by 10\\% and established many commercial partnerships with suppliers."
 
)

```

```{r}

# Spanish

spanish_degrees <- tribble(
  ~degree, ~start, ~end, ~institution, ~location,
  "Maestría en Administración de Negocios", 2018, 2018, "CENTRUM - PONTIFICIA UNIVERSIDAD CATÓLICA DEL PERÚ", "Lima, Perú",
  "Administración de Negocios Globales", 2018, 2018, "MAASTRICHT UNIVERSITY", "Maastricht, Países Bajos",
  "Administración de Negocios Globales", 2018, 2018, "UNIVERSITY OF VICTORIA", "Victoria, B.C., Canadá",
  "Ingeniería Industrial", 2014, 2014, "PONTIFICIA UNIVERSIDAD CATÓLICA DEL PERÚ", "Lima, Perú",
)

spanish_certifs <- tribble(
  ~degree,
  "\\textbf{Google Data Analytics} | Google | 2021",
  "\\textbf{Google Project Management} | Google | 2021",
  "\\textbf{Especialización en Deep Learning} | DeepLearning.AI | 2020",
  "\\textbf{Analítica de Negocios y Gestión de la Información} | CENTRUM - Pontificia Universidad Católica del Perú | 2016"
)

spanish_teaching <- tribble(
  ~experience,
  "\\textbf{Google Data Analytics} | Google | 2021",
  "\\textbf{Google Project Management} | Google | 2021",
  "\\textbf{Especialización en Deep Learning} | DeepLearning.AI | 2020",
  "\\textbf{Analítica de Negocios y Gestión de la Información} | Centrum Católica | 2016"
)

spanish_skills <- tribble(~skill,
        "\\textbf{Idiomas:} Inglés, Español, Portugués",
        "\\textbf{Gestión de proyectos:} Metodologías ágiles, Scrum, Kanban",
        "\\textbf{Gestión financiera:} Gestión de P\\&L, análisis financiero y presupuestario, control de costos ",
        "\\textbf{Gestión estratégica y operativa:} Gestión del cambio, transformación digital, optimización de cadena de suministro",
        "\\textbf{Gestión comercial y de marketing:} Estrategias comerciales y de marketing, gestión de proveedores, análisis de mercado",
        "\\textbf{Análisis de datos / Machine Learning:} SQL, Python (pandas, numpy, scikit-learn, TensorFlow), R (tidyverse, shiny)",
        "\\textbf{Visualización de datos / IDEs:} Looker, Tableau, Power BI, Visual Studio Code, RStudio, Colab, Jupyter Notebooks",
        "\\textbf{Herramientas colaborativas / CRM / ERP:} Google Docs, Trello, Asana, Slack, Teams, Salesforce, Jira, SAP, Oracle",
        "\\textbf{Cloud / Otros:} Google Cloud, Amazon Web Services, Microsoft Azure, Docker, Kubernetes, Airflow, Git, Spark, Regex, DAX",
)

spanish_soft_skills <- tribble(~skill,
        "\\textbf{Liderazgo:} Amplia capacidad para inspirar y motivar equipos hacia el logro de objetivos en común.",
        "\\textbf{Comunicación:} Excelentes habilidades de comunicación interpersonal, facilitando la colaboración.",
        "\\textbf{Resolución de problemas:} Enfoque analítico para identificar y resolver problemas complejos de manera eficiente.",
        "\\textbf{Mentoría y capacitación:} Experiencia en enseñanza y mentoría, promuevo el desarrollo profesional y personal.",
        "\\textbf{Gestión del tiempo:} Habilidad para priorizar tareas y manejar múltiples proyectos bajo presión."
)

spanish_hobbies <- tribble(~description,
        "Comparto contenido educativo en datos y analítica para una comunidad de más de 80k seguidores en redes sociales.",
        "Siempre estoy con actitud positiva y optimista, me encanta transmitir energías positivas con las personas que me rodean.",
        "Participo en causas de Diversidad, Equidad e Inclusión (DEI) en el trabajo y comunidad por medio de liderazgo inclusivo.",
        "Me encanta viajar y conocer nuevas culturas, he tenido la oportunidad de visitar 27 países y vivir en el extranjero.",
        "Me fascina la historia, disfruto aprendiendo de eventos históricos, civilizaciones antiguas y visitar museos."
)

# English

english_degrees <- tribble(
  ~degree, ~start, ~end, ~institution, ~location,
  "Master in Business Administration", 2018, 2018, "CENTRUM CATOLICA", "Lima, Peru",
  "Global Business Administration", 2018, 2018, "MAASTRICHT UNIVERSITY", "Maastricht, Netherlands",
  "Global Business Administration", 2018, 2018, "UNIVERSITY OF VICTORIA", "Victoria, B.C., Canada",
  "Industrial Engineer", 2014, 2014, "PONTIFICIA UNIVERSIDAD CATOLICA DEL PERU", "Lima, Peru",
)

english_certifs <- tribble(~degree,
  "\\textbf{Google Data Analytics} | Google | 2021",
  "\\textbf{Google Project Management} | Google | 2021",
  "\\textbf{Deep Learning Specialization} | DeepLearning.AI | 2020",
  "\\textbf{Data Management and Analytics} | Centrum Católica | 2016"
)

english_teaching <- tribble(
  ~experience,
  "\\textbf{Google Data Analytics} | Google | 2021",
  "\\textbf{Google Project Management} | Google | 2021",
  "\\textbf{Especialización en Deep Learning} | DeepLearning.AI | 2020",
  "\\textbf{Analítica de Negocios y Gestión de la Información} | Centrum Católica | 2016"
)

english_skills <- tribble(~skill,
        "\\textbf{Languages:} English, Spanish, Portuguese",
        "\\textbf{Project management:} Agile methodologies, Scrum, Kanban",
        "\\textbf{Financial management:} P\\&L management, financial and budget analysis, cost control",
        "\\textbf{Strategic and operational management:} Change management, digital transformation, supply chain optimization",
        "\\textbf{Commercial & Marketing:} Commercial & marketing strategies, vendor management, market analysis",
        "\\textbf{Data analysis / Machine Learning:} SQL, Python (pandas, numpy, scikit-learn, TensorFlow), R (tidyverse, shiny)",
        "\\textbf{Data visualization / IDEs:} Looker, Tableau, Power BI, Visual Studio Code, RStudio, Colab, Jupyter Notebooks",
        "\\textbf{Collaborative tools / CRM / ERP:} Google Docs, Trello, Asana, Slack, Teams, Salesforce, Jira, SAP, Oracle",
        "\\textbf{Cloud / Others:} Google Cloud, Amazon Web Services, Microsoft Azure, Docker, Kubernetes, Airflow, Git, Spark, Regex, DAX",
)

english_soft_skills <- tribble(~skill,
        "\\textbf{Leadership:} Strong ability to inspire and motivate teams toward common goals.",
        "\\textbf{Communication:} Excellent interpersonal communication skills, fostering collaboration.",
        "\\textbf{Problem solving:} Analytical approach to efficiently identify and resolve complex problems.",
        "\\textbf{Mentoring & training:} Teaching and mentoring experience, promoting personal and professional growth.",
        "\\textbf{Time management:} Ability to prioritize tasks and manage multiple projects under pressure."
)

english_hobbies <- tribble(~description,
        "I share educational content on data and analytics with a community of over 80k followers on social media.",
        "I'm always positive and optimistic, and I love spreading good energy to those around me.",
        "I actively support Diversity, Equity & Inclusion (DEI) causes at work and in my community through inclusive leadership.",
        "I love to travel and explore new cultures, I've had the opportunity to visit 27 countries and live abroad",
        "I'm passionate about history and enjoy learning about historical events, ancient civilizations, and visiting museums."
)

# Remote

remote_degrees <- tribble(
  ~degree, ~start, ~end, ~institution, ~location,
  "Master in Business Administration", 2018, 2018, "CENTRUM CATOLICA", "Lima, Peru",
  "Program in Global Business Administration", 2018, 2018, "MAASTRICHT UNIVERSITY", "Maastricht, Netherlands",
  "Program in Global Business Administration", 2018, 2018, "UNIVERSITY OF VICTORIA", "Victoria, B.C., Canada",
  "Industrial Engineer", 2014, 2014, "PONTIFICIA UNIVERSIDAD CATOLICA DEL PERU", "Lima, Peru",
)

remote_certifs <- tribble(~degree,
  "\\textbf{Google Data Analytics} | Google | 2021",
  "\\textbf{Google Project Management} | Google | 2021",
  "\\textbf{Deep Learning Specialization} | DeepLearning.AI | 2020",
  "\\textbf{Data Management and Analytics} | Centrum Católica | 2016"
)

remote_teaching <- tribble(
  ~experience,
  "\\textbf{Google Data Analytics} | Google | 2021",
  "\\textbf{Google Project Management} | Google | 2021",
  "\\textbf{Especialización en Deep Learning} | DeepLearning.AI | 2020",
  "\\textbf{Analítica de Negocios y Gestión de la Información} | Centrum Católica | 2016"
)

remote_skills <- tribble(~skill,
        "\\textbf{Languages:} English, Spanish, Portuguese",
        "\\textbf{Data Science / Machine Learning:} SQL, Python (pandas, numpy, TensorFlow), R (tidyverse)",
        "\\textbf{Web Design / Development:} HTML, CSS, Javascript, PHP, WordPress",
        "\\textbf{IDEs:} Visual Studio Code, RStudio, Google Colab, Jupyter Notebooks",
        "\\textbf{Collaborative tools:} Google Docs, Trello, Asana, Slack, Teams",
        "\\textbf{Visualization tools:} Looker, Tableau, Data Studio, Power BI",
        "\\textbf{CRM / Support tools:} Salesforce, Freshdesk, Jira, Kustomer",
        "\\textbf{Cloud computing:} Google Cloud, Amazon Web Services, Microsoft Azure",
        "\\textbf{Others:} Docker, Git, Kubernetes, Airflow, Spark, Regex, LaTeX, Markdown, Visual Basic, DAX",
        "\\textbf{ERPs:} SAP, Oracle"
)

remote_soft_skills <- tribble(~skill,
        "\\textbf{Leadership:} Extensive ability to inspire and motivate teams towards achieving common goals.",
        "\\textbf{Communication:} Excellent interpersonal communication skills, facilitating collaboration.",
        "\\textbf{Problem solving:} Analytical approach to identifying and efficiently resolving complex problems.",
        "\\textbf{Mentoring and training:} Experience in teaching and mentoring, promoting professional and personal development.",
        "\\textbf{Time management:} Ability to prioritize tasks and manage multiple projects under pressure."
)

remote_hobbies <- tribble(~description,
        "I always maintain a positive and optimistic attitude, and I love to share positive energy with those around me.",
        "I participate in Diversity, Equity, and Inclusion (DEI) causes at work and in the community through inclusive leadership.",
        "I love to travel and experience new cultures, having had the opportunity to visit 27 countries and live abroad.",
        "I typically walk a lot, averaging 10,000 steps daily for the past 18 months, and I maintain an active lifestyle.",
        "I am fascinated by history and enjoy learning about historical events, ancient civilizations, and visiting museums."
)

```

```{r}
# Select the appropriate set of titles, companies, and bullets
if (lang == "English") {
    sections <- english_sections
    summary <- english_summary
    titles <- english_titles
    companies <- english_companies
    bullets <- english_bullets
    degrees <- english_degrees
    certifs <- english_certifs
    project_titles <- english_project_titles
    project_bullets <- english_project_bullets
    teaching <- english_teaching
    skills <- english_skills
    soft_skills <- english_soft_skills
    hobbies <- english_hobbies
  } else if (lang == "Spanish") {
    sections <- spanish_sections
    summary <- spanish_summary
    titles <- spanish_titles
    companies <- spanish_companies
    bullets <- spanish_bullets
    degrees <- spanish_degrees
    certifs <- spanish_certifs
    project_titles <- spanish_project_titles
    project_bullets <- spanish_project_bullets
    teaching <- spanish_teaching
    skills <- spanish_skills
    soft_skills <- spanish_soft_skills
    hobbies <- spanish_hobbies
  } else if (lang == "Remote") {
    sections <- remote_sections
    summary <- remote_summary
    titles <- remote_titles
    companies <- remote_companies
    bullets <- remote_bullets
    degrees <- remote_degrees
    certifs <- remote_certifs
    project_titles <- remote_project_titles
    project_bullets <- remote_project_bullets
    teaching <- remote_teaching
    skills <- remote_skills
    soft_skills <- remote_soft_skills
    hobbies <- remote_hobbies
  } else {
    stop("Language error.")
  }
```

\thispagestyle{empty}

\smallskip

\vspace{-0.5cm}

\hspace{0.25cm}\color{black}{\Large\faInfoCircle}\hspace{0.25cm}\section{`r sections[1]`}

\vspace{-0.25cm}

```{r summary, results='asis'}
tribble(~description,
        paragraph(summary[1]),
        "\\tiny"
        ) %>%
        tabular()
```

\vspace{-0.375cm}

\hspace{0.25cm}\color{black}{\Large\faBriefcase}\hspace{0.25cm}\section{`r sections[2]`}

\vspace{-0.375cm}

```{r experience, results='asis'}
tribble(~position, ~start, ~end,

# Nota: Si hay error aquí es por los putos porcentajes        

        # Position
        title(titles[1]), 2024, 2024,
        company(companies[1]), 2024, 2024,
        bullet(bullets[1]), 2024, 2024,
        bullet(bullets[2]), 2024, 2024,
        bullet(bullets[3]), 2024, 2024,
        bullet(bullets[4]), 2024, 2024,
        "\\tiny", 2024, 2024,

        # Position
        title(titles[2]), 2021, 2024,
        company(companies[2]), 2021, 2024,
        bullet(bullets[5]), 2021, 2024,
        bullet(bullets[6]), 2021, 2024,
        bullet(bullets[7]), 2021, 2024,
        bullet(bullets[8]), 2021, 2024,
        bullet(bullets[9]), 2021, 2024,
        "\\tiny", 2021, 2024,

        # Position
        title(titles[3]), 2021, 2021,
        company(companies[3]), 2021, 2021,
        bullet(bullets[10]), 2021, 2021,
        bullet(bullets[11]), 2021, 2021,
        bullet(bullets[12]), 2021, 2021,
        bullet(bullets[13]), 2021, 2021,
        "\\tiny", 2021, 2021,

        # Position
        title(titles[4]), 2020, 2021,
        company(companies[4]), 2020, 2021,
        bullet(bullets[14]), 2020, 2021,
        bullet(bullets[15]), 2020, 2021,
        bullet(bullets[16]), 2020, 2021,
        "\\tiny", 2020, 2021,

        # Position
        title(titles[5]), 2018, 2019,
        company(companies[5]), 2018, 2019,
        bullet(bullets[17]), 2018, 2019,
        bullet(bullets[18]), 2018, 2019,
        "\\tiny", 2018, 2019,

        # Position
        title(titles[6]), 2013, 2018,
        company(companies[6]), 2013, 2018,        
        bullet(bullets[19]), 2013, 2018,
        bullet(bullets[20]), 2013, 2018,
        "\\tiny", 2013, 2018,

        ) %>%
        arrange(-start) %>%
        mutate(end = replace_na(as.character(end), "")) %>%
        mutate(years = if_else(end==start,
                                as.character(start),
                                paste(start, "--", end, sep=""))) %>%
        select(years, position) %>%
        group_by(years) %>%
        mutate(n = row_number()) %>%
        mutate(years = case_when(n>1 ~ "", TRUE ~ years)) %>%
        mutate(years = case_when(n==2 ~ location(degrees$location[1]), TRUE ~ years)) %>%
        mutate(aux = str_detect(years,'^20*')) %>%
        mutate(years = case_when(aux==TRUE ~ calendar(years), TRUE ~ years)) %>%
        select(position, years) %>%
        ungroup() %>%
        mutate(final=paste(position, years, sep="")) %>%
        select(final) %>%
        tabular()
```

\vspace{-0.375cm}

\hspace{0.25cm}\color{black}{\Large\faGraduationCap}\hspace{0.25cm}\section{`r sections[3]`}

\vspace{-0.25cm}

```{r education, results='asis'}
tribble(~degree, ~start, ~end,

        title(degrees$degree[1]), degrees$start[1], degrees$end[1],
        company(degrees$institution[1]), degrees$start[1], degrees$end[1],
        "\\tiny", degrees$start[1], degrees$end[1],

        title(degrees$degree[2]), degrees$start[2], degrees$end[2],
        company(degrees$institution[2]), degrees$start[2], degrees$end[2],
        company(degrees$institution[3]), degrees$start[3], degrees$end[3],
        "\\tiny", degrees$start[2], degrees$end[2],

        title(degrees$degree[4]), degrees$start[4], degrees$end[4],
        company(degrees$institution[4]), degrees$start[4], degrees$end[4],
        "\\tiny", degrees$start[4], degrees$end[4],

        ) %>%
        arrange(-start) %>%
        mutate(end = replace_na(as.character(end), "")) %>%
        mutate(years = if_else(end==start,
                                as.character(start),
                                paste(start, "--", end, sep=""),
                                paste(start, "--", end, sep="")
                                )) %>%
        select(years, degree) %>%
        mutate(r = case_when(grepl('textbf', degree) ~ row_number())) %>%
        fill(r, .direction = c('down')) %>%
        group_by(years, r) %>%
        mutate(n = row_number()) %>%
        mutate(years = case_when(n>1 ~ "", TRUE ~ years)) %>%
        mutate(years = case_when(
                    grepl(degrees$institution[1], degree) ~ location(degrees$location[1]),
                    grepl(degrees$institution[2], degree) ~ location(degrees$location[2]),
                    grepl(degrees$institution[3], degree) ~ location(degrees$location[3]),
                    grepl(degrees$institution[4], degree) ~ location(degrees$location[4]),
                    TRUE ~ years)) %>%
        mutate(aux = str_detect(years,'^20*')) %>%
        mutate(years = case_when(aux==TRUE ~ calendar(years), TRUE ~ years)) %>%
        select(degree, years) %>%
        ungroup() %>%
        mutate(final=paste(degree, years, sep="")) %>%
        select(final) %>%
        tabular()
```

\vspace{-0.5cm}

\hspace{0.25cm}\color{black}{\Large\faUniversity}\hspace{0.25cm}\section{`r sections[4]`}

\vspace{-0.10cm}

```{r certificates, results='asis'}
tribble(~degree,
        bullet(certifs$degree[1]),
        bullet(certifs$degree[2]),
        bullet(certifs$degree[3]),
        bullet(certifs$degree[4]),
        "\\tiny"
        ) %>%
        tabular()
```

\vspace{-0.1cm}

\hspace{0.25cm}\color{black}{\Large\faList}\hspace{0.25cm}\section{`r sections[5]`}

\vspace{-0.1cm}

```{r projects, results='asis'}
tribble(~project,
    
    # Proyecto 1
    title(project_titles[1]), 
    company(project_bullets[1]), 
    bullet(project_bullets[2]), 
    "\\tiny", 
    
    # Proyecto 2
    title(project_titles[2]), 
    company(project_bullets[3]), 
    bullet(project_bullets[4]),
    "\\tiny",
    
    # Proyecto 3
    title(project_titles[3]),
    company(project_bullets[5]),
    bullet(project_bullets[6]),
    "\\tiny",
    
    # Proyecto 4
    title(project_titles[4]), 
    company(project_bullets[7]), 
    bullet(project_bullets[8]),
    "\\tiny",
    
    # Proyecto 5
    title(project_titles[5]),
    company(project_bullets[9]),
    bullet(project_bullets[10]),
    "\\tiny",
    
  ) %>%
  tabular()
```

\vspace{-0.1cm}

\hspace{0.25cm}\color{black}{\Large\faBook}\hspace{0.25cm}\section{`r sections[6]`}

\vspace{-0.1cm}

```{r technical_skills, results='asis'}
tribble(~skill,
        bullet(skills$skill[1]),
        bullet(skills$skill[2]),
        bullet(skills$skill[3]),
        bullet(skills$skill[4]),
        bullet(skills$skill[5]),
        bullet(skills$skill[6]),
        bullet(skills$skill[7]),
        bullet(skills$skill[8]),
        bullet(skills$skill[9]),
        "\\tiny"
        ) %>%
        tabular()
```

\vspace{-0.1cm}

\hspace{0.25cm}\color{black}{\Large\faComment}\hspace{0.25cm}\section{`r sections[7]`}

\vspace{-0.1cm}

```{r soft_skills, results='asis'}
tribble(~skills,
        bullet(soft_skills$skill[1]),
        bullet(soft_skills$skill[2]),
        bullet(soft_skills$skill[3]),
        bullet(soft_skills$skill[4]),
        bullet(soft_skills$skill[5]),
        "\\tiny"
        ) %>%
        tabular()
```

\vspace{-0.1cm}

\hspace{0.25cm}\color{black}{\Large\faBalanceScale}\hspace{0.25cm}\section{`r sections[8]`}

\vspace{-0.1cm}

```{r interests, results='asis'}
tribble(~hobbies,
        bullet(hobbies$description[1]),
        bullet(hobbies$description[2]),
        bullet(hobbies$description[3]),
        bullet(hobbies$description[4]),
        bullet(hobbies$description[5]),
        "\\tiny"
        ) %>%
        tabular()
```

\thispagestyle{empty}
